---
title: "Weight of Fish"
author: "Salena Bennett"
date: "Spring 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```
```{r}
Fishdata=read.csv(file="Fish.csv")
```



# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Perch
## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Perchdata = filter(Fishdata, Species=="Perch")
Perchdata = subset (Perchdata, select = -Species)
```



## Inferential Results


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perchdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

The best one is the one that uses two variables: H, and W.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

```{r}
best.model <- lm(Weight~Length2+Height,data=Perchdata)
fullup <- lm(Weight~.,data=Perchdata)
summary(best.model)
```

The P-value here is so small the you did not get this model by chance, it is an excellent fit.

```{r}
anova(fullup,best.model)
```



<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

The P-value is 0.879 which means that there is really no difference between using the model that has all of the data vs. the model that is only using two variables.

# Bream
## Methods

```{r}
Breamdata = filter(Fishdata, Species=="Bream")
Breamdata = subset (Breamdata, select = -Species)
```

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->



## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Breamdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

The best model is the one that uses three variables: L1, H, W.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length2+Height,data=Breamdata)
fullup <- lm(Weight~.,data=Breamdata)
summary(best.model)
```

```{r}
anova(fullup,best.model)
```

The P-value is to large to say that there is a difference between utilizing the best model which utilizes three variables and the best model that utilizes two.

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->




# Smelt
## Methods

```{r}
Smeltdata = filter(Fishdata, Species=="Smelt")
Smeltdata = subset (Smeltdata, select = -Species)
```

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->



## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smeltdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

The model that is the best is the one that uses four variables: L1, L2, H, and W.


```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[4,]
```

```{r}
best.model <- lm(Weight~Length2+Width,data=Smeltdata)
fullup <- lm(Weight~.,data=Smeltdata)
summary(best.model)
```

```{r}
anova(fullup,best.model)
```

The P-valuse is to large to large to say that there is a difference between the best model that uses four variables and the best model that uses two variables

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the Georgetown videos collection.!-->

Based on the automated selection of variables there is no real difference in using a model using two variables versus using one with all variables. This this was identified through a graphical depiction adjusted rsquare as well as the pvalues. The conclusion comparing the pvalues of the variable models were all so small that I rejected the null hypothesis and these models are beneficial in predicting weight of the fish . The pvaules associated with the anovas were large therefor result in a failure to reject the null hypothesis, there is no difference using the model with two variable versus the fullup models.

